## Against the whole genome
```{r setup-vfdb, eval=TRUE, include=FALSE, echo=FALSE}
## Convert to factors
blast <- vfdb_blast_genome
colnames(blast) <- c("Contig", "Start", "End", "Strand", "Gene", "Coverage_aln", "Gaps", "Coverage %", "Identity %", "Database", "VFDB gene id", "Virulence Factor", "Description")
blast$`Virulence Factor` <- gsub(blast$`Virulence Factor`, pattern = "\\[", replacement = "")
blast$`Virulence Factor` <- gsub(blast$`Virulence Factor`, pattern = "\\]", replacement = "")
blast$`Virulence Factor` <- gsub(blast$`Virulence Factor`, pattern = "_", replacement = " ")
vfs <- str_split(blast$`Virulence Factor`, " ")
blast$`Virulence Factor ID` <- sapply(vfs, tail, 1)
blast$`Virulence Factor ID` <- gsub(blast$`Virulence Factor ID`, pattern = "\\(", replacement = "")
blast$`Virulence Factor ID` <- gsub(blast$`Virulence Factor ID`, pattern = "\\)", replacement = "")
```


All the virulence factors in VFDB database that have an alignment against the genome full-filling the thresholds set are shown in Table \@ref(tab:write-table-vfdb-genome). We report both annotations using the predicted genes and the whole genome because Prokka uses prodigal to predicted genes which may miss some genomes.

The following virulence factors were detected (having one or more genes in the genome):

> The results are showed as: **VFDB virulence factor name (VFDB virulence factor ID)**.

```{r results='asis'}
string.list <- apply(blast, 1, function (x) {
  if (grepl("VF.*[0-9]+", x[14])) {
    name <- x[12]
    id <- x[14]
    url <- paste0("[", name, "]", "(http://www.mgc.ac.cn/cgi-bin/VFs/vfs.cgi?VFID=", id, "#", id, ")")
  } else {
    name <- x[12]
    id <-  str_split(x[11], "\\(")[[1]][1]
    url <- paste0("[", name, "]", "(http://www.mgc.ac.cn/cgi-bin/VFs/comp_gene.cgi?RID=", id, ")")
  }
  
  return(url)
}) %>% sort() %>% unique()
cat("- Virulence factors found in the query genome:\n")
cat(paste("\t-", string.list), sep = '\n')
```

<caption>(#tab:write-table-vfdb-genome) Virulence factors annotated using the Victors database via BLASTn against the whole genome</caption>
```{r}
# Get urls
## VFs
blast$`Virulence Factor` <- apply(blast, 1, function (x) {
  if (grepl("VF.*[0-9]+", x[14])) {
    id <- x[14]
    name <- x[12]
    url <- paste0("http://www.mgc.ac.cn/cgi-bin/VFs/vfs.cgi?VFID=", id, "#", id)
    url <- paste0('<a  target=_blank href=', url, '>', name,'</a>' )
  } else {
    id <-  str_split(x[11], "\\(")[[1]][1]
    name <- x[12]
    url <- paste0("http://www.mgc.ac.cn/cgi-bin/VFs/comp_gene.cgi?RID=", id)
    url <- paste0("<a  target=_blank href=", url, ">", name,"</a>" )
  }
  
  return(url)
})

## Genes
blast$`VFDB gene id` <- apply(blast, 1, function (x) {
  
  id <-  str_split(x[11], "\\(")[[1]][1]
  name <- x[11]
  url <- paste0("http://www.mgc.ac.cn/cgi-bin/VFs/comp_gene.cgi?RID=", id)
  url <- paste0("<a  target=_blank href=", url, ">", name,"</a>" )
    
  return(url)
})

# Render dt
blast[sapply(blast, is.character)] <- lapply(blast[sapply(blast, is.character)], as.factor)
datatable(blast,
          escape = FALSE,
          filter = 'top',
          options = dt_opt_lst,
          extensions = 'Buttons',
          rownames = T)
```

## Against the predicted genes

```{r parsing-db, eval=TRUE, include=FALSE, echo=FALSE}
# Function to get Attribute Fields
getAttributeField <- function (x, field, attrsep = ";") { 
  s = strsplit(x, split = attrsep, fixed = TRUE) 
  sapply(s, function(atts) { 
    a = strsplit(atts, split = "=", fixed = TRUE) 
    m = match(field, sapply(a, "[", 1)) 
    if (!is.na(m)) { rv = a[[m]][2] 
    } 
    else { 
      rv = as.character(NA) 
    } 
    return(rv) 
  }) 
}

# Function to get VF IDs
vf_id_url <- function (x) {
  if (grepl("VF.*[0-9]+", x[8])) {
    id <- x[8]
    url <- paste0("http://www.mgc.ac.cn/cgi-bin/VFs/vfs.cgi?VFID=", id, "#", id)
  } else {
    id <-  str_split(x[4], "\\(")[[1]][1]
    url <- paste0("http://www.mgc.ac.cn/cgi-bin/VFs/comp_gene.cgi?RID=", id)
  }
  
  return(url)
}

# Function to get URLs for VF List
vf_id_url_list <- function (x) {
  if (grepl("VF.*[0-9]+", x[8])) {
    name <- x[5]
    id <- x[8]
    url <- paste0("[", name, "]", "(http://www.mgc.ac.cn/cgi-bin/VFs/vfs.cgi?VFID=", id, "#", id, ")")
  } else {
    name <- x[5]
    id <-  str_split(x[4], "\\(")[[1]][1]
    url <- paste0("[", name, "]", "(http://www.mgc.ac.cn/cgi-bin/VFs/comp_gene.cgi?RID=", id, ")")
  }
  
  return(url)
}

# Function do get URLs for DATATABLE
vf_id_url_DT <- function (x) {
  if (grepl("VF.*[0-9]+", x[8])) {
    id <- x[8]
    url <- paste0("http://www.mgc.ac.cn/cgi-bin/VFs/vfs.cgi?VFID=", id, "#", id)
    url <- paste0('<a  target=_blank href=', url, '>', id,'</a>' )
  } else {
    id <-  str_split(x[4], "\\(")[[1]][1]
    url <- paste0("http://www.mgc.ac.cn/cgi-bin/VFs/comp_gene.cgi?RID=", id)
    url <- paste0("<a  target=_blank href=", url, ">", id,"</a>" )
  }
  
  return(url)
}

# Create ID Column
gff$ID <- getAttributeField(as.character(gff$V9), "ID", ";")

# To upper
gff$ID <- toupper(gff$ID)

# Sort entries
vfdb_blast <- vfdb_blast[order(vfdb_blast$qseqid),]

# Data Complete
full_info <- merge.data.frame(vfdb_blast, gff, by.x = "qseqid", by.y = "ID")

# Create Position Column
full_info$position <- paste(full_info$V1, ":", full_info$V4, "-", full_info$V5, sep = "")

# Parse BLAST
blast <- full_info %>% select(qseqid, stitle, position)
blast <- separate(blast, stitle, c("vf_header", "Description"), sep = " ", extra = "merge")
blast <- separate(blast, vf_header, c("db", "Gene Name", "ref", "Virulence Factor Name"), sep = "~~~", extra = "merge")
blast$`Virulence Factor Name` <- gsub(blast$`Virulence Factor`, pattern = "\\[", replacement = "")
blast$`Virulence Factor Name` <- gsub(blast$`Virulence Factor`, pattern = "\\]", replacement = "")
blast$`Virulence Factor Name` <- gsub(blast$`Virulence Factor`, pattern = "_", replacement = " ")
vfs <- str_split(blast$`Virulence Factor Name`, " ")
blast$`Virulence Factor ID` <- sapply(vfs, tail, 1)
blast$`Virulence Factor ID` <- gsub(blast$`Virulence Factor ID`, pattern = "\\(", replacement = "")
blast$`Virulence Factor ID` <- gsub(blast$`Virulence Factor ID`, pattern = "\\)", replacement = "")

# Sort
blast <- arrange(blast, `Virulence Factor ID`, `Gene Name`)

# Get urls
urls <- apply(blast, 1, vf_id_url)
```

All virulence factors (from VFDB) that were found to have at least one gene in the query genome are shown in the list below. All of them are linked to the database for further investigations.

> The results are showed as: **VFDB virulence factor name (VFDB virulence factor ID)**.

```{r results='asis'}
string.list <- apply(blast, 1, vf_id_url_list) %>% sort() %>% unique()
cat("- Virulence factors found in the query genome:\n")
cat(paste("\t-", string.list), sep = '\n')
```

All query genes predicted by Prokka that have a match in VFDB are more detailed in Table \@ref(tab:vfdb-table). Additionally, Figure \@ref(fig:vfs-png) summarizes the amount of annotated genes of each virulence factor. Information are always linked to the database to make investigations easier.

```{r vfs-png, fig.align='center', fig.show='hold', fig.cap="Virulence Factors annotated from [VFDB](http://www.mgc.ac.cn/VFs/main.htm) database", out.width="45%"}
summary <- blast %>%
  select("Virulence Factor Name", "Gene Name")
colnames(summary) <- c("Virulence_Factor_Name", "Gene_Name")
vfs <- plyr::count(summary, "Virulence_Factor_Name")
ggplot(vfs, aes(x=Virulence_Factor_Name, y=freq, fill=Virulence_Factor_Name)) + geom_bar(stat = "identity") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  xlab("Virulence Factors") +
  ylab("Number of annotated genes") +
  guides(fill=guide_legend(title = "Virulence Factors"))
```

<caption>(#tab:vfdb-table) Virulence factors annotated using the VFDB database via BLASTn</caption>
```{r}
# Produce Table
colnames(blast) <- c("Query Protein ID", "Database", "Gene Name", "Ref", "Virulence Factor Name", "Description", "Query Protein Coordinates", "VF ID")
blast$`VF ID` <- apply(blast, 1, vf_id_url_DT)
## The conversion
blast[sapply(blast, is.character)] <- lapply(blast[sapply(blast, is.character)], as.factor)
datatable(blast %>% select("Virulence Factor Name", "VF ID", "Gene Name", "Description", "Query Protein ID", "Query Protein Coordinates"),
          escape = FALSE,
          filter = 'top',
          options = dt_opt_lst,
          extensions = 'Buttons',
          rownames = T)
```